\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-01-18 src/thesis.tex
Added more stuff to chapter 2. see diff.
chapter 2 in edit still. see diff for changes.
partative set theory TBD in chapter 2. beginning to work on chapter 3 now.
Started cleaning up chapter 3. Deferring it though to work on Chapter 2. Need to accommodate N's new proofs for removal of algorithmic charac.
See diff for other changes left out in this comment.
Fixed a bug in chapter 2 (from last commit). Endnotes in chap 2 changed to footnotes. Tucker matrices coded. Tikz is going to be the way of the graphics in Infinite Jest.
first draft of PQR trees done. next is cert algo and icpia.

\usepackage{../lib/mythesislib}
\usepackage{../lib/mylatexlib}
\usepackage{thesisfiguresandtables} % Code for tables are in this
                                % package if it is too long to inline
                                % in .tex file.

% \usepackage{comment}         % DEBUG ONLY
%\includeonly{020chap2}         % DEBUG ONLY 
%\includeonly{0021ded}         % DEBUG ONLY

\def \mythesissubmissiondate {10 January 2012}
\def \mythesissubmissionmonth {\MakeUppercase {January 2012}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title page
%
\title{\mythesistitleNOTSYNPOSIS} \author{\myname} \date{
  {\mythesissubmissionmonth}}
\department{\MakeUppercase{\mythesisdept}}
\maketitle

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dedication?
%
\include{0021ded}

@@

\include{010chap1}
% turning counter reset. perhaps universal endnote counter is good?
% being schizo about it now. DECIDE! ENDNOTEMARKS DEPEND ON IT.
\setcounter{endnote}{0} % need to empty the file too. how?! -
                        % FIXED. turns out, just having notes is
                        % enough. or maybe it was fluke.
\include{020chap2}
\include{030chap3}
\include{040chap4}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices.
%
% \appendix %%% NON NEIN NAHI ILLA NONE
% \chapter{A}
% \newpage

>>>>

\usepackage{../lib/mylatexlib}
\usepackage{../lib/mythesislib}
\usepackage{thesisfiguresandtables} % Code for tables are in this
                                % package if it is too long to inline
                                % in .tex file.
%\usepackage[inline] 
%\usepackage[margins] 
\usepackage[finalnew]
         {../lib/trackchanges} % For tracking changes.
                               % :Package options:
                               % [finalold]
                               %   Ignore all of the edits. 
                               %   The document will look as if
                               %   the edits had not been added. 
                               % [finalnew]
                               %   Accept all of the edits. 
                               %   Notes will not be shown in the
                               %   final output. 
                               % [footnotes]
                               %   Added text will be shown
                               %   inline. Removed text and notes
                               %   will be shown as footnotes.  
                               %   This is the default option.
                               % [margins]
                               %   Added text will be shown
                               %   inline. Removed text and notes
                               %   will be shown in the
                               %   margin. Margin notes will be
                               %   aligned with the edits when
                               %   possible. 
                               % [inline]
                               %   All changes and notes will be
                               %   shown inline.

\addeditor{fyi}                % use "fyi" - for general notes with no
%                                 action points.
\addeditor{important}          % needs attention level 2
\addeditor{dire}               % needs attention level infinity NOW!
\addeditor{minor}              % least priority TBDs that
                               %  need to go into thesis  
\addeditor{pressing}           % needs attention level 1

% \usepackage{comment}         % DEBUG ONLY
\includeonly{020chap2}         % DEBUG ONLY 
%\includeonly{030chap3,050appa}         % DEBUG ONLY 
%\includeonly{0031ded}         % DEBUG ONLY

\def \mythesissubmissiondate {13 January 2012}
\def \mythesissubmissionmonth {\MakeUppercase {January 2012}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title page
%
\title{\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization
  of Consecutive Ones Property of Binary Matrices''}}% 
\author{\myname}% 
\date{{\mythesissubmissionmonth}}%
\department{\MakeUppercase{\mythesisdept}}
\maketitle

\nocite{*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dedication?
%
\include{0031ded}%{0021ded}

@@

\include{010chap1}
% turning counter reset. perhaps universal endnote counter is good?
% being schizo about it now. DECIDE! ENDNOTEMARKS DEPEND ON IT.
%\setcounter{endnote}{0} % need to empty the file too. how?! -
                        % FIXED. turns out, just having notes is
                        % enough. or maybe it was fluke.
\include{020chap2}
\include{030chap3}
\include{040chap4}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices.
%
\appendix %%% NON NEIN NAHI ILLA NONE. But maybe.
\include{050appa}

%\newpage
